Transfer report

### 2018-12-11 Report/final-results.Rmd
Small change to the talbe output

```{r}
df <- only_blocks(walk_all, c(6)) %>% group_by(condition) %>% summarize(dist = mean(min_norm_distance, na.rm=T), errors= mean(errors, na.rm=T))
kable(df, caption='Average performance in all conditions in the last block in visitation errors and walking disntace', digits=2)
```

>>>>

```{r}
df <- only_blocks(walk_all, c(6)) %>% group_by(condition) %>% summarize(dist =m_sd_report(min_norm_distance), errors= m_sd_report(errors))
kable(df, caption='Average performance in all conditions in the last block in visitation errors and walking disntace', digits=2)
```
